Research Proposal

### 2021-10-05 Reports/JOURNAL - Confidence Regions/ResearchProposal.tex
:alien:

If $\alpha,\beta>0$, we can relate the $\text{db}(\alpha,\beta, n_{\text{top}},\zeta)$ model with the (continuous) Beta distribution in the following manner:
\begin{equation}
\Pr(X=x \mid \alpha, \beta, n_{\text{top}}, \zeta) = 
\frac{1}{\kappa} f\Big(
\frac{x-n_{\text{bot}}+1}{n_{\text{top}}-n_{\text{bot}}+2}
\Big),
\label{Eq:Probdb}
\end{equation}
where
$$
\kappa = \sum_{i=n_{\text{bot}}}^{n_{\text{bot}}} f\Big(
\frac{x-n_{\text{bot}}+1}{n_{\text{top}}-n_{\text{bot}}+2}
\Big),
$$
and $f$ is the density of a Beta distribution with parameters $\alpha$ and $\beta$, i.e.,
\begin{equation}
	f(u;\alpha, \beta) = \frac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)} u^{\alpha-1} (1-u)^{\beta-1} \mathbbm 1_{(0,1)}(u).
	\label{Eq:DensBeta}
\end{equation}
Denote this situation $U\sim\text{Beta}(\alpha,\beta)$.

@@

If $U\sim\text{Beta}(\alpha,\beta)$, then its entropy is
\begin{equation}
H(U) = \log\text{B}(\alpha,\beta) -
(\alpha-1)\psi(\alpha) -(\beta-1) \psi(\beta) +(\alpha+\beta-2) \psi(\alpha+\beta),
\label{Eq:HBeta}
\end{equation}
in which we denoted
$$
\text{B}(\alpha,\beta) = \frac{\Gamma(\alpha)\Gamma(\beta)}{\Gamma(\alpha+\beta)}.
$$

Also, if $U_1\sim\text{Beta}(\alpha_1,\beta_1)$ and
$U_2\sim\text{Beta}(\alpha_2,\beta_2)$, then the Kullback-Leibler divergence between the models is
\begin{multline}
D_{\text{KL}}(U_1,U_2) = \log\frac{\text{B}(\alpha_2,\beta_2)}{\text{B}(\alpha_1,\beta_1)} +
(\alpha_2-\alpha_1) \psi(\alpha) +
(\beta_2-\beta_1) \psi(\beta) + \\
(\alpha_2-\alpha_1+\beta_2-\beta_1) \psi(\alpha_1+\beta_1).
\label{Eq:DKLBeta}
\end{multline}
With~\eqref{Eq:DKLBeta} we may obtain the Jensen-Shannon distance between $U\sim\text{Beta}(\alpha,\beta)$ and the Uniform distribution that is $V\sim\text{Beta}(1,1)$.
The product between~\eqref{Eq:HBeta} and this Jensen-Shannon distance is the complexity.

>>>>

If $\alpha,\beta>0$, we can relate the $\text{db}(\alpha,\beta, n_{\text{top}},\zeta)$ model with the (continuous) Beta distribution in the following manner:
\begin{equation}
\Pr(X=x \mid \alpha, \beta, n_{\text{top}}, \zeta) = 
\frac{1}{\kappa} f\Big(
\frac{x-n_{\text{bot}}+1}{n_{\text{top}}-n_{\text{bot}}+2}
\Big),
\label{Eq:Probdb}
\end{equation}
where
$$
\kappa = \sum_{i=n_{\text{bot}}}^{n_{\text{bot}}} f\Big(
\frac{x-n_{\text{bot}}+1}{n_{\text{top}}-n_{\text{bot}}+2}
\Big),
$$
and $f$ is the density of a Beta distribution with parameters $\alpha$ and $\beta$, i.e.,
\begin{equation}
	f(v;\alpha, \beta) = \frac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)} v^{\alpha-1} (1-v)^{\beta-1} \mathbbm 1_{(0,1)}(v).
	\label{Eq:DensBeta}
\end{equation}
Denote this situation $V\sim\text{Beta}(\alpha,\beta)$.

@@

If $V\sim\text{Beta}(\alpha,\beta)$, then its entropy is
\begin{equation}
H(V) = \log\text{B}(\alpha,\beta) -
(\alpha-1)\psi(\alpha) -(\beta-1) \psi(\beta) +(\alpha+\beta-2) \psi(\alpha+\beta),
\label{Eq:HBeta}
\end{equation}
in which we denoted
$$
\text{B}(\alpha,\beta) = \frac{\Gamma(\alpha)\Gamma(\beta)}{\Gamma(\alpha+\beta)}.
$$
We propose approximating the distribution of $\mathfrak{H}$ by the distribution of 
\begin{equation}
\widehat{H}(V)= \log\text{B}(\widehat\alpha,\widehat\beta) -
(\widehat\alpha-1)\psi(\widehat\alpha) -(\widehat\beta-1) \psi(\widehat\beta) +(\widehat\alpha+\widehat\beta-2) \psi(\widehat\alpha+\widehat\beta),
\end{equation}
which is a transformation of a bivariate Gaussian distribution.

Also, if $V_1\sim\text{Beta}(\alpha_1,\beta_1)$ and
$V_2\sim\text{Beta}(\alpha_2,\beta_2)$, then the Kullback-Leibler divergence between the models is
\begin{multline}
D_{\text{KL}}(V_1,V_2) = \log\frac{\text{B}(\alpha_2,\beta_2)}{\text{B}(\alpha_1,\beta_1)} +
(\alpha_2-\alpha_1) \psi(\alpha) +
(\beta_2-\beta_1) \psi(\beta) + \\
(\alpha_2-\alpha_1+\beta_2-\beta_1) \psi(\alpha_1+\beta_1).
\label{Eq:DKLBeta}
\end{multline}
With~\eqref{Eq:DKLBeta} we may obtain the Jensen-Shannon distance between $V\sim\text{Beta}(\alpha,\beta)$ and the Uniform distribution that is $U\sim\text{Beta}(1,1)$.
The product between~\eqref{Eq:HBeta} and this Jensen-Shannon distance is the complexity.
Our proposal consists in approximating the distribution of $\mathfrak{C}$ by the distribution of $\widehat{C}(V,U)$.
